Chronic conditions and increased antibiotic consumption

### 2017-03-31 chronic-conditions/chronic-condition-drivers.Rmd
added all years multivar

>>>>

## On all years

It seems like the multivariate model is the easiest one to understand and interpret. I therefore ran this one analysis on all the years.

```{r}
year_model = function(y) {
  bene_fn = sprintf('../bene_%i.tsv', y)
  pde_fn = sprintf('../pde_%i.tsv', y)
  cc_fn = sprintf('../../data/cc_%i.tsv', y)

  bene = read_tsv(bene_fn) %>%
    filter(hmo_months==0, age >= 65) %>%
    mutate(is_female=sex=='female', is_white=race=='white') %>%
    select(bene_id, age, is_female, is_white, state)
  chronic_conditions = read_tsv(cc_fn) %>%
    rename(bene_id=BENE_ID) %>%
    select(-STRCTFLG) %>%
    mutate_at(vars(AMI:HYPOTH), function(x) x==3)
  pde = read_tsv(pde_fn) %>%
    count(bene_id) %>% rename(n_claims=n)

  usage = bene %>%
    left_join(census_regions, by='state') %>%
    left_join(chronic_conditions, by='bene_id') %>%
    left_join(pde, by='bene_id') %>%
    replace_na(list(n_claims=0))

  multivariate_res = usage %>%
    glm(multivariate_formula, data=., family='poisson') %>%
    broom::tidy() %>%
    mutate(label=y)

  multivariate_res
}

yearly_models = lapply(2011:2014, year_model) %>%
  bind_rows
```

```{r}
#yearly_models %>%
#  select(term, label, estimate) %>%
#  spread(label, estimate) %>%
#  arrange(desc(`2011`)) %>%
#  kable
```

```{r}
term_levels = yearly_models %>%
  filter(label==2011) %>%
  arrange(desc(estimate)) %$%
  rev(term)

yearly_models %>%
  mutate(term=factor(term, levels=term_levels, ordered=TRUE)) %>%
  ggplot(aes(x=term, y=estimate, color=factor(label))) +
  geom_point() +
  coord_flip() +
  theme_minimal()
```
